---
title: 'Yelp Reviews Analysis: Las Vegas'
output:
  html_document:
    df_print: paged
---


For Project of Course: Social Network Analysis
Team Members: Kumar Bipulesh, Taranpreet Singh

In the first part analysis on Restaurants in the Las vegas has been done.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(stringr)
library(ggmap)
df <- read_csv("vegasRst.csv")
glimpse(df)
#5902,9
#businessId/ name
summary(df)
```
 
##### Key points - 
Average rating: 3.45

Closed Restaurants: 33%

Avg Review count: 157

Next, The relation between business_ids and business_names is analyzed.
```{r}

nlevels(as.factor(df$categories))
#3601 cats
nlevels(as.factor(df$business_id))
#5902
nlevels(as.factor(df$business_name))
#4300
# some businesses with more than 1 business id

df %>% select(business_name) %>% group_by(business_name) %>%
  count() %>%  arrange(desc(n)) %>% head(10)


```

We can see that some businesses names have more than 1 business_ids, this is due to food chains such as KFC, etc

##### Stars Distribution
```{r message=FALSE, warning= F}
# stars count
df %>% select(stars) %>% group_by(stars) %>%
  count() %>%  arrange(desc(stars))

# histogram
ggplot(df, aes(x=stars)) + geom_histogram() + ggtitle("Distribution of Stars") #+ th

```

To see how the resaturants are ranked a new variable score is created by multiplying stars with review counts. For initial exploration we have not considered the Time factor while creating score for each restaurant.
Top rated reataurants and restaurants with least rated.
```{r}
df$score <- df$stars * df$review_count
summary(df$score)

#by business -top
df %>% select(business_name,score) %>% group_by(business_name) %>% 
  summarise( avg = mean(score), count = n()) %>%  arrange(desc(avg)) %>% head(5)
 
# single place businesses lead

df %>% select(business_name,score) %>% group_by(business_name) %>% 
  summarise( avg = mean(score),count= n()) %>%  arrange(avg) %>% 
  head(10) 

```

Top rated closed restaurants

```{r}
df %>% select(business_name,score,is_open) %>%  arrange(desc(score)) %>% 
  filter(is_open==0) %>%  head(10)
```

##### Geo-spatial analysis

```{r message=FALSE, warning=FALSE,error=F}

#Geo spatial analysis
#ggplot(df,aes(longitude,latitude, color=stars)) + geom_point() 
#Filtering points
df %>% filter(latitude > 35.95 & latitude < 36.4 & longitude > -115.37 & longitude < -115) %>% 
  ggplot(aes(longitude,latitude, color=stars)) + geom_point() 

#coordinates of vegas
#36.1699 N, 115.1398 W

vegas <- c(lon = -115.1398, lat = 36.1699)

# 
map <- get_map(vegas, zoom = 11, scale = 1)

ggmap(map) 

mapdf <- df %>% 
  filter(latitude > 35.95 & latitude < 36.4 & longitude > -115.37 & longitude < -115)

ggmap(map) + geom_point(aes(longitude,latitude, color=stars), data = mapdf)


```

Part 2

##### Exploration of restaurants reviews
```{r message =FALSE, include =FALSE}

dfRev <- read_csv("vegasRstRev.csv")
# 929636,9

```

```{r}
glimpse(dfRev)
#key business_id
summary(dfRev)
#?? funny cool useful

# date range # 2005-01-24 2017-12-11 

nlevels(as.factor(dfRev$business_id))
#5902 businesses
nlevels(as.factor(dfRev$user_id))
#337874 users
```

```{r}
#users with high number of reviews
dfRev %>% select(user_id) %>% group_by(user_id) %>%  summarise(count = n()) %>% 
  arrange(desc(count)) %>%  head(10)
#bLbSNkLggFnqwNNzzq-Ijw  1175

dfRev %>% select(business_id) %>% group_by(business_id) %>%  summarise(count = n()) %>% 
  arrange(desc(count)) %>%  head(10)

```

Time series

```{r}
#number of reviews on particular date
dfRev %>% select(review_id,date) %>% group_by(date) %>% 
  summarise(count=n()) %>% arrange(desc(count)) %>% head()

#time series plot 
dfRev %>% select(review_id,date) %>% group_by(date) %>% 
  summarise(count=n()) %>%
  ggplot(aes(x=date,y=count)) + geom_line(color='darkorange',alpha=0.8)

# From 2015
dfRev %>% select(review_id,date) %>% filter(date > as.Date('2015-01-01')) %>% group_by(date) %>% 
  summarise(count=n()) %>% 
  ggplot(aes(x=date,y=count)) + geom_line(color='darkorange',alpha=0.8,size=0.3) 


```


Word counts
```{r warning = FALSE}
# word count average for +3 reviews
dfRev$wc <- str_count(dfRev$text)
#
mean(dfRev$wc)
#612


mean(dfRev$wc[dfRev$stars>3])
# 560.0811

mean(dfRev$wc[dfRev$stars<3])
#709.8648

mean(dfRev$wc[dfRev$stars>4])
# 500.0811

mean(dfRev$wc[dfRev$stars<2])
# 676

ggplot(dfRev,aes(x=date,y=wc)) + geom_line(color='darkorange',alpha=0.3,size=0.2) 

```

##### Fake id's

```{r message =FALSE, include=F, warning=FALSE}
usr <- read_csv("vegasUsers.csv")


```

```{r}
str5 <- usr %>% select(user_id,review_count,average_stars,yelping_since) %>% 
  filter(average_stars==5,review_count > 25) %>% 
  arrange(desc(review_count))  %>% select(user_id,average_stars,review_count)


fake_ids <- dfRev %>% select(user_id,business_id) %>% 
  filter(user_id %in% unlist(str5$user_id)) %>%
  group_by(user_id) %>% summarise( BsnsReviwed = n_distinct(business_id)) %>% 
  filter(BsnsReviwed<3) %>% arrange(BsnsReviwed) 


fake_ids <- left_join(fake_ids,str5)

fake_ids %>% arrange(desc(review_count)) %>% head()


```





